---
title: "hw622_1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

open libraries

```{r}
library(tidymodels)
library(tidyverse)
```

load data from github

```{r}
small.r<-read_csv('https://raw.githubusercontent.com/sconnin/Model_Compare/main/5000%20HRA%20Records.csv')
large.r<-read_csv('https://raw.githubusercontent.com/sconnin/Model_Compare/main/500000%20HRA%20Records.csv')
```

data overview 

```{r}

#first five rows

head(small.r)

# data types

str(small.r)

# dataframe summary

summary(small.r)
summary(large.r)


```
Data Key

Education
1 'Below College'
2 'College'
3 'Bachelor'
4 'Master'
5 'Doctor'

EnvironmentSatisfaction
1 'Low'
2 'Medium'
3 'High'
4 'Very High'

JobInvolvement
1 'Low'
2 'Medium'
3 'High'
4 'Very High'

JobSatisfaction
1 'Low'
2 'Medium'
3 'High'
4 'Very High'

PerformanceRating
1 'Low'
2 'Good'
3 'Excellent'
4 'Outstanding'

RelationshipSatisfaction
1 'Low'
2 'Medium'
3 'High'
4 'Very High'

WorkLifeBalance
1 'Bad'
2 'Good'
3 'Better'
4 'Best'
